\subsection{Development Approach}
The project followed an incremental design process: the database schema was
designed and normalised first, followed by DDL implementation, then PL/SQL
logic, and finally the Java JDBC frontend. Each layer was tested independently
before integration.

\subsection{Tools and Technologies}
\begin{itemize}
    \item \textbf{Database:} Oracle 21c XE (XEPDB1) for schema hosting,
          constraint enforcement, and PL/SQL execution.
    \item \textbf{Connectivity:} Oracle JDBC Type-4 thin driver
          (\texttt{ojdbc11.jar}) for Java--database communication.
    \item \textbf{Frontend:} JavaFX for the graphical user interface,
          providing a dark-themed tabbed dashboard.
    \item \textbf{Build Tool:} Apache Maven for dependency management
          and compilation.
    \item \textbf{IDE:} IntelliJ IDEA for development and debugging.
\end{itemize}

\subsection{Database Design Process}
The original Exercise 6.21 E-R schema was analysed to identify entities
relevant to a shopping cart context. Extensions were then designed to cover
the full purchase lifecycle, including Cart, Inventory, Orders, Order Items,
and Payment entities. Each table was verified against 3NF before DDL was
written.

\subsection{Implementation Sequence}
\begin{enumerate}
    \item Schema design and normalisation.
    \item DDL: table definitions, constraints, and sequences.
    \item Sample data insertion across all 11 tables.
    \item PL/SQL: functions, procedures, and triggers.
    \item JDBC layer: connection setup, query execution, and procedure calls.
    \item JavaFX UI: one tab per core operation, with a live console log.
    \item Testing against all scenarios in Table~5.
\end{enumerate}

\subsection{Transaction Strategy}
All multi-step write operations --- particularly checkout --- use manual
transaction control (\texttt{setAutoCommit(false)}) with explicit
\texttt{COMMIT} on success and \texttt{ROLLBACK} in the exception handler,
ensuring atomicity across order placement, inventory decrement, and payment
recording.